|

### 2024-08-11 doc/paper.qmd
finalise replicated table

Table 1 provides descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score, where countries are sorted in descending order based on their aggregate score. The discussion on replication findings is presented in @sec-results.
```{python}
#| label: final_table 
#| echo: false
#| output: asis

print(prep_latex_table(
    em_results['final_table'],
    caption='Replicated table - EM1, EM2, EM3, EM4, and Aggregate EM Score',
    label='tab:final_table'
))
```

```{python}
#| label: summary_stats 
#| echo: false
#| output: asis

print(prep_latex_table(
    em_results['summary_stats'],
    caption='Replicated table - Summary Statistics for EM1, EM2, EM3, and EM4',
    label='tab:summary_stats'
))
```

>>>>

Table 1 provides descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score, where countries are sorted in descending order based on their aggregate score. The discussion on replication findings is presented in @sec-results.
```{python}
#| label: final_combined_table
#| echo: false
#| output: asis

print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - EM1, EM2, EM3, EM4, Aggregate EM Score, and Summary Statistics',
    label='tab:final_combined_table'
))
```
